---
#citeproc: no
graphics: yes
name: Juan David
surname: Leong贸mez
position: "Associate Professor"
address: "Faculty of Psychology, Universidad El Bosque"
phone: (+57) 601-6489000 Ext. 1901
www: jdleongomez.info
profilepic: "../JDL.jpg"
email: "jleongomez@unbosque.edu.co"
github: JDLeongomez
aboutme: |
  I am a scientist mainly interested in human behaviour, as well as quantitative methods and reproducible science.
date: "`r Sys.setlocale('LC_TIME','English');format(Sys.Date(),'%d %B, %Y')`"
header-includes: \usepackage{multicol}
  \usepackage{xurl}
  \RequirePackage{fancyhdr}
  \usepackage{fontawesome}
  \usepackage{xcolor}
  \usepackage{hyperref}
  \hypersetup{
    colorlinks,
    urlcolor=teal}
csl: "csl/apa7-cv.csl"
headcolor: 207373
nocite: "@*"
knit: bookdown::render_book
bibliography_featured: "../featured.bib"
bibliography_featured_preprint: "../featured_preprint.bib"
---

```{r setup, include=FALSE, cache = FALSE}
library(knitr)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(RefManageR)
RefManageR::BibOptions(check.entries = FALSE,
           bib.style = "authoryear",
           sorting = "",
           cite.style = "alphabetic",
           sorting = "ydnt",
           style = "markdown",
           hyperlink = TRUE,
           dashed = FALSE)

library(vitae)
library(tidyverse)
library(ezpickr)
```

# About me

I am an Associate Professor and Researcher at the [Human Behaviour Lab (LACH)](https://www.psicologia.unbosque.edu.co/lach), [Faculty of Psychology](https://www.uelbosque.edu.co/psicologia), at [Universidad El Bosque](https://www.uelbosque.edu.co/) in Bogota, Colombia. My research interests include mate choice and human vocal communication, with an aspiration towards understanding musicality. I am also interested in hormonal effects on human behaviour. I published among the first articles showing within-individual changes in voice pitch in response to the social status of the listener, and have demonstrated strong effects of voice modulation on listeners in courtship contexts. I am very passionate about quantitative methods and **R** programming, as a tool to promote reproducibility and open science.

# Skills

\begin{cvskills}
  \cvskill
    {Programming}
    {R (advanced: all data wrangling, analysis, plots and tables -and even this CV- made in R)}

  \cvskill
    {Reproducible Report}
    {Markdown/Rmarkdown (including {\fontfamily{cmr}\selectfont\LaTeX} and HTML\faHtml5)}

  \cvskill
    {Quantitative Research}
    {General and Generalised Models, Linear Mixed-effects Models, Model selection and Averaging, Machine Learning}

  \cvskill
    {Software}
    {R, RStudio, Praat, Audacity, InkScape, Zotero, OBS Studio, Blender}

  \cvskill
    {Languages}
    {English/Spanish (native)}
\end{cvskills}

# Education

```{r education}
ezpickr::pick("data/education.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

# Working and Teaching Experience

For a full list, and a description of responsibilities, please check [my website](https://jdleongomez.info/en/#experience) or my [detailed CV](https://jdleongomez.info/en/files/jdl_cv_en.pdf).

```{r working-experience}
ezpickr::pick("data/working-experience.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

# Accomplishments

For information on **grants**, **scholarships**, **awards** and **prizes**, please check [my website](https://jdleongomez.info/en/#accomplishments) or my [detailed CV](https://jdleongomez.info/en/files/jdl_cv_en.pdf).

# Selected Publications

For a full list, please check the publications section on [my website](https://jdleongomez.info/en/publication/) or my [detailed CV](https://jdleongomez.info/en/files/jdl_cv_en.pdf). 

\begin{footnotesize}
\textbf{Note:} I am the/a corresponding author in all these publications
\end{footnotesize}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_featured}
:::
\endgroup

# Investigaci贸n Abierta (YouTube channel)

[\textcolor{red}{\faYoutubePlay} Investigaci贸n Abierta](https://www.youtube.com/c/Investigaci贸nAbierta) [\textit{Open Research}] is a YouTube channel (in Spanish) where I post videos and tutorials related to quantitative research methods and open science, as well as useful open source software.

# Postgraduate Supervision

For a full list, including undergraduate supervision, please check [my website](https://jdleongomez.info/en/team/#students) or my [detailed CV](https://jdleongomez.info/en/files/jdl_cv_en.pdf).

```{r supervision}
ezpickr::pick("data/supervision.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

# Editorial Appointments

I recently served as a guest editor of a 2-part theme issue on [Philosophical Transactions B](https://royalsocietypublishing.org/journal/rstb) (check [Part 1](https://royalsocietypublishing.org/toc/rstb/2021/376/1840), [Part 2](https://royalsocietypublishing.org/toc/rstb/2022/377/1841)). I have served as an \textit{ad-hoc} reviewer for a variety of journals including [Proceedings of the Royal Society B: Biological Sciences](https://royalsocietypublishing.org/journal/rspb), [Royal Society Open Science](https://royalsocietypublishing.org/journal/rsos), [Evolution and Human Behavior](https://www.sciencedirect.com/journal/evolution-and-human-behavior), [Scientific Reports](https://www.nature.com/srep/), [Basic and Applied Social Psychology](https://www.tandfonline.com/toc/hbas20/current), [Cortex}](https://www.journals.elsevier.com/cortex), [Perception](https://journals.sagepub.com/home/pec),
[Evolutionary Psychology](https://journals.sagepub.com/home/evp), and [Frontiers in Psychology](https://www.frontiersin.org/journals/psychology) where I am currently a [Review Editor](https://loop.frontiersin.org/people/438954/overview) for the [\textit{Evolutionary Psychology specialty section}](https://www.frontiersin.org/journals/psychology/sections/evolutionary-psychology).  My full, verified review record is available from my [Web of Science](https://www.webofscience.com/wos/author/record/387716) profile.

<!-- *`r Sys.Date()`* -->
