---
#citeproc: no
graphics: yes
name: Juan David
surname: Leongómez
position: "Associate Professor"
address: "Faculty of Psychology, Universidad El Bosque"
phone: +57-1 6489000 Ext. 1901
www: jdleongomez.info
profilepic: "../JDL.jpg"
email: "jleongomez@unbosque.edu.co"
github: JDLeongomez
aboutme: |
  I am a scientist mainly interested in human behaviour, as well as quantitative methods, and reproducible science.
date: "`r Sys.setlocale('LC_TIME','English');format(Sys.Date(),'%d %B, %Y')`"
header-includes: \usepackage{multicol}
csl: "csl/apa7-cv.csl"
headcolor: 008080
nocite: "@*"
knit: bookdown::render_book
bibliography_journals: "../journal.bib"
bibliography_divulgation: "../divulgation.bib"
bibliography_working_paper: "../working_paper.bib"
bibliography_IA: "../IA.bib"
---

```{r setup, include=FALSE, cache = FALSE}
library(knitr)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(RefManageR)
RefManageR::BibOptions(check.entries = FALSE,
           bib.style = "authoryear",
           sorting = "",
           cite.style = "alphabetic",
           sorting = "ydnt",
           style = "markdown",
           hyperlink = TRUE,
           dashed = FALSE)

library(vitae)
library(tidyverse)
library(ezpickr)
library(vitae)
library(ggplot2)
library(emojifont)
library(fontawesome)
library(rworldmap)
library(dplyr)
library(sf)
library(stplanr)
```

# About me

I am an Associate Professor and Researcher at the **Human Behaviour Lab (LACH)**, [\textcolor{teal}{Faculty of Psychology}](https://www.uelbosque.edu.co/psicologia), at [\textcolor{teal}{Universidad El Bosque}](https://www.uelbosque.edu.co/) in Bogota, Colombia. My research interests include mate choice and human vocal communication, with an aspiration towards understanding musicality. I am also interested in bioacoustics and psychoacoustics, as well as hormonal effects on human behaviour. I published among the first articles showing within-individual changes in voice pitch in response to the social status of the listener, and have demonstrated strong effects of voice modulation on listeners in courtship contexts. I am very passionate about quantitative methods and R programming, as a tool to promote reproducibility and open science.

# Primary Research Methods

\begin{multicols}{2}
\begin{itemize}
 \item Experimental designs
 \item Online questionnaires 
 \item Voice recording
 \item Acoustic analysis
 \item Facial photographs
 \item Geometric morphometrics
 \item Anthropometry
 \item Reproducible Research
\end{itemize}
\end{multicols}

# Skills

\begin{cvskills}
  \cvskill
    {Programming}
    {R (advanced: all data wrangling, analysis, plots and tables -and even this CV- made in R)}

  \cvskill
    {Reproducible Reports}
    {Markdown/Rmarkdown (including {\fontfamily{cmr}\selectfont\LaTeX} and HTML\faHtml5)}

  \cvskill
    {Quantitative Research}
    {General and Generalised Models, Linear Mixed-effects Models, Model selection and Averaging, Machine Learning}

  \cvskill
    {Software}
    {R, RStudio, Praat, Audacity, InkScape, Mendeley, Zotero}

  \cvskill
    {Languages}
    {English/Spanish (native)}
\end{cvskills}

# Research Areas

 * Human voice
 * Vocal modulation
 * Mate choice
 * Human behaviour
 * Hormones and behaviour

# Education

```{r education}
ezpickr::pick("data/education.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

# Working Experience

```{r working-experience}
ezpickr::pick("data/working-experience.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

# Teaching Experience

```{r teaching-experience}
ezpickr::pick("data/teaching-experience.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

# Scholarships, Awards and Honors

```{r award}
ezpickr::pick("data/award.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

# Grants

```{r grant}
ezpickr::pick("data/grant.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

# Publications

## \textcolor{teal}{Preprints and Articles under Review}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_working_paper}
:::
\endgroup

## \textcolor{teal}{Published Journal Articles and Works}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_journals}
:::
\endgroup

## \textcolor{teal}{Divulgation articles}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_divulgation}
:::
\endgroup

# Investigación Abierta (YouTube channel)

[\textcolor{teal}{Investigación Abierta}](https://www.youtube.com/user/juanleongomez/featured) is a YouTube channel (in Spanish) where I post videos and tutorials related to quantitative research methods and open science, as well as useful open source software.

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_IA}
:::
\endgroup

# Conference Presentations, Posters and Workshops

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

`r knitr::knit_child("data/poster.txt")`

\endgroup

# Postgraduate and undergraduate Supervision

```{r supervision}
ezpickr::pick("data/supervision.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

# Editorial Appointments

My verified review record is available from my [\textcolor{teal}{Publons}](https://publons.com/researcher/1333339/juan-david-leongomez/) profile. 

```{r service}
ezpickr::pick("data/service.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

# Scientific Events

```{r event}
ezpickr::pick("data/event.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

# Memberships

## Current

  * [\textcolor{teal}{International Society for Human Ethology (ISHE)}](https://ishe.org/)

## Past

  * [\textcolor{teal}{European Human Behaviour and Evolution Association (EHBEA)}](https://www.cambridge.org/core/membership/ehbea)
  * [\textcolor{teal}{Association for Psychological Science (APS)}](https://www.psychologicalscience.org/)

<!-- *`r Sys.Date()`* -->
