---
#citeproc: no
graphics: yes
name: Juan David
surname: Leongómez
position: "Associate Professor"
address: "Faculty of Psychology, Universidad El Bosque"
phone: (+57) 319 407 7102
www: jdleongomez.info
profilepic: "../JDL.jpg"
email: "jleongomez@unbosque.edu.co"
github: JDLeongomez
aboutme: |
  I am a scientist mainly interested in human behaviour, as well as quantitative methods and reproducible science.
date: "`r Sys.setlocale('LC_TIME','English');format(Sys.Date(),'%d %B, %Y')`"
header-includes: \usepackage{multicol}
  \usepackage{xurl}
  \usepackage{fontawesome}
  \usepackage{xcolor}
  \usepackage{hyperref}
  \hypersetup{
    colorlinks,
    urlcolor=teal}
csl: "csl/apa7-cv.csl"
headcolor: 008080
nocite: "@*"
knit: bookdown::render_book
bibliography_journals: "../journal.bib"
bibliography_divulgation: "../divulgation.bib"
bibliography_working_paper: "../working_paper.bib"
bibliography_IA: "../IA_en.bib"
---

```{r setup, include=FALSE, cache = FALSE}
library(knitr)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(RefManageR)
RefManageR::BibOptions(check.entries = FALSE,
           bib.style = "authoryear",
           sorting = "",
           cite.style = "alphabetic",
           sorting = "ydnt",
           style = "markdown",
           hyperlink = TRUE,
           dashed = FALSE)

library(vitae)
library(tidyverse)
library(ezpickr)
library(vitae)
library(ggplot2)
library(emojifont)
library(fontawesome)
library(rworldmap)
library(dplyr)
library(sf)
library(stplanr)
```

# Highlights

**About me:** I currently am an Associate Professor and Researcher at the [Human Behaviour Lab (LACH)](https://www.psicologia.unbosque.edu.co/lach), [Faculty of Psychology](https://www.uelbosque.edu.co/psicologia), at [Universidad El Bosque](https://www.uelbosque.edu.co/) in Bogota, Colombia. I hold a Bachelor's in Music Education from Universidad Pedagógica Nacional (Colombia), an MSc in Evolutionary Psychology from the University of Liverpool, and a PhD from the University of Stirling.

**Research:** I study the evolutionary underpinnings of human behaviour, particularly those related to mate choice and the social effects of vocal signals, with a particular interest in the evolution of musicality. I have published among the first articles showing within-individual changes in voice pitch in response to the social status of the listener and have demonstrated strong effects of voice modulation on listeners in courtship contexts.

\underline{\textit{Voice modulation special issue}}: More recently, I have led the edition of the 2-part theme issue [\textit{Voice modulation: from origin and mechanism to social impact}](https://jdleongomez.info/en/files/TB1840-1841_voice_modulation.pdf) for *Philosophical Transactions of the Royal Society B* (parts 1 and 2 publishing online on November 1 and 15, 2021, respectively). This 2-part issue constitutes the first compendium of research on voice modulation. It includes articles covering the diverse functions of voice modulation in human and nonhuman nonverbal communication, from signalling motivation and emotion, exaggerating biological traits like body size and masculinity, to enabling song and musicality across cultures. This issue contains three articles in which I am an author, including one in which we propose a bold new model for the evolution of musicality embedded in the context of human voice modulation (Leongómez, Havlíček, & Roberts, [2021](https://jdleongomez.info/en/publication/leongomez2021musicality/)).

**Open science:** I strongly support the dissemination of open science practices and the use of opensource software and programming as tools to promote transparency and reproducibility, as well as to reduce national inequalities in production of, and access to, scientific knowledge. Because of this, I have been heavily involved in the teaching and designing of statistics-related modules, with an emphasis on open science and reproducibility.

# Research Interests

```{=tex}
\begin{multicols}{2}
\begin{itemize}
 \item Human voice
 \item Vocal modulation 
 \item Mate choice
 \item Human behaviour
 \item Psychoacoustics
 \item Hormone effects on human behaviour
\end{itemize}
\end{multicols}
```

# Primary Research Methods

```{=tex}
\begin{multicols}{2}
\begin{itemize}
 \item Experimental designs
 \item Online questionnaires 
 \item Voice recording
 \item Acoustic analysis
 \item Facial photographs
 \item Geometric morphometrics
 \item Anthropometry
 \item Reproducible Research
\end{itemize}
\end{multicols}
```

# Skills

```{=tex}
\begin{cvskills}
  \cvskill
    {Programming}
    {R (advanced: all data wrangling, analysis, plots and tables -and even this CV and \href{https://jdleongomez.info}{my website}- made in R)}

  \cvskill
    {Reproducible Reports}
    {Markdown/Rmarkdown (including {\fontfamily{cmr}\selectfont\LaTeX} and HTML\faHtml5), Version Control (GitHub, GitLab)}

  \cvskill
    {Quantitative Research}
    {General and Generalised Models, Linear Mixed-effects Models, Model selection and Averaging, Machine Learning}

  \cvskill
    {Software}
    {R, RStudio, Praat, Audacity, InkScape, Mendeley, Zotero, OBS Studio, Blender (video editing)}

  \cvskill
    {Languages}
    {English/Spanish (native)}
\end{cvskills}
```

# Higher Education

```{r education}
ezpickr::pick("data/education.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why,
                          .protect = FALSE)
```

# Working Experience (University Level)

I have administrative and leadership responsibility both within the University and externally. Within the University, I am the leader of the research group [Procesos Cognoscitivos y Educación](https://investigaciones.unbosque.edu.co/procesos-cognoscitivos-y-educacion) [Cognitive Processes and Education], being in charge of the periodic calls for the [recognition and measurement of research, technological development or innovation groups](https://minciencias.gov.co/convocatorias/fortalecimiento-capacidades-para-la-generacion-conocimiento/convocatoria-nacional-para) by the Colombian Ministry of Science, Technology and Innovation ([Minciencias](https://minciencias.gov.co/)), I have been Module Organiser for 9 modules, and sit on two Faculty committees. Externally, I carry editorial responsibilities and review funding applications for [Minciencias](https://minciencias.gov.co/).

```{r working-experience}
ezpickr::pick("data/working-experience.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why,
                          .protect = FALSE)
```

Before working at universities, I worked as a private piano teacher to adult students (2000 - 2005), and taught music-related topics in several institutions in Colombia, at different levels ranging from nursery to secondary school (2003 - 2006), as well as the school of the Colombian Youth Philharmonic Orchestra (2005 - 2006). In 2006 I moved to the UK to study English and look for postgraduate opportunities.

# Teaching Experience (University Level)

I have been mostly involved in teaching statistics-related modules[^1]. At both Universidad El Bosque (MSc level) and Universidad de La Sabana (undergraduate level), I redesigned the statistics learning programmes to integrate teaching of statistical techniques with the use of statistical software. Since 2017, I have led an initiative at Universidad El Bosque to move from proprietary software like SPSS, to open-source software, following open science principles and focusing on statistical modelling, inference, and reproducibility. This has included using *jamovi* for both undergraduate and postgraduate courses, as well as running R seminars for staff and co-designing an optional R module for undergraduate students.

[^1]: In Colombia, academic years run between January and December, and all university courses are organised in semesters, tipically starting in February and August. Because of this, each year of teaching means running the same module twice.

```{r teaching-experience}
ezpickr::pick("data/teaching-experience.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

## \textbf{Student evaluations} (Universidad El Bosque)

Below are evaluations of some representative modules I have taught. Please be aware of the different system established by the University to evaluate modules for undergraduate and postgraduate students.

```{r student-evaluations}
ezpickr::pick("data/student-evaluations.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why,
                          .protect = FALSE)
```

## \textbf{Student comments} (Universidad El Bosque)

Below are some anonymous comments included during student evaluations for modules I have taught.

```{r student-comments}
ezpickr::pick("data/student-comments.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why,
                          .protect = FALSE)
```

# Scholarships, Prizes and Awards

```{r award}
ezpickr::pick("data/award.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

# Grants

I have received over U\$200,000 in independent research funding from external grants and scholarships since the start of my PhD, including from major funder [Minciencias](https://minciencias.gov.co/#) (Ministry of Science, Technology and Innovation of Colombia).

```{r grant}
ezpickr::pick("data/grant.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

# Publications

```{r include=FALSE}
library(scholar)
library(ggplot2)
library(ggpubr)
library(ggtext)

jd <- "8Q0jKHsAAAAJ"

ct <- get_citation_history(jd)
pt <- c(1,1,0,1,2,0,2,3,4,1,8)
get_num_articles(jd)
profile <- get_profile(jd)

dat <- cbind(ct, pt)

ylim.prim <- c(0, max(dat$pt)*1.25)   # publications
ylim.sec <- c(0, max(dat$cites)*1.2)   # citations

b <- diff(ylim.prim)/diff(ylim.sec)
a <- ylim.prim[1] - b*ylim.sec[1]

Sys.setlocale('LC_TIME','English')

p1 <- ggplot(dat, aes(year, pt)) +
  geom_col(fill = "lightgrey") +
  geom_line(aes(y = a + cites*b), color = "#008080") +
  scale_y_continuous("Publications", sec.axis = sec_axis(~ (. - a)/b, name = "Citations")) +
  theme_pubclean() +
  theme(axis.line.y.right = element_line(color = "#008080"), 
        axis.ticks.y.right = element_line(color = "#008080"),
        axis.text.y.right = element_text(color = "#008080"), 
        axis.title.y.right = element_text(color = "#008080"),
        axis.line.y.left = element_line(color = "black"), 
        axis.ticks.y.left = element_line(color = "black"),
        axis.text.y.left = element_text(color = "black"), 
        axis.title.y.left = element_text(color = "black"),
        plot.subtitle=element_text(size=9)) +
  theme(axis.text = element_text(size = 6),
        axis.title = element_text(size = 8)) +
  labs(x = "Year",
       subtitle = "Publications and citations per year")

library(scales)
library(xfun)

yearRecent <- as.integer(format(Sys.Date(),'%Y')) - 2

citSum <- profile$total_cites

citRecentSum <- ct %>%
  summarize(sumB = sum(cites[year >= yearRecent]))

count50cit <- nrow(ct[ct$cites > 50, ])

citRecentProp <- citRecentSum/citSum

#g-index
pubs <- get_publications(jd)
pubs$square <- as.numeric(row.names(pubs))^2
pubs$sums <- cumsum(pubs$cites)
gindex <- max(which(pubs$square < pubs$sums))

pubs$rank <- seq.int(nrow(pubs))

p2 <- ggplot(pubs, aes(x = rank, y = cites)) +
  geom_segment(aes(x = profile$h_index, y = 0, xend = profile$h_index, yend = profile$h_index+4),
               size = 0.1, color = "#008080") +
  geom_line(size = 1, colour = "grey") +
  geom_abline(intercept = 0, slope = 1, colour = "#008080", linetype = "dashed") +
  annotate("text", y = profile$h_index, x = profile$h_index,
           label= paste0("h-index"),
           hjust = -0.5, angle = 90,
           color = "#008080", size = 2.5) + 
  labs(x = "Rank", 
       y = "Citations",
       subtitle = "Citations per publication and h-index") + 
  xlim(c(0, nrow(pubs)-4)) +
  theme_pubclean() +
  theme(axis.line.y.left = element_line(color = "black"), 
        axis.ticks.y.left = element_line(color = "black"),
        axis.text.y.left = element_text(color = "black"), 
        axis.title.y.left = element_text(color = "black"),
        axis.text = element_text(size = 6),
        axis.title = element_text(size = 8),
        plot.subtitle = element_text(size = 9))

p.fin <- ggarrange(p2, p1,
                   widths = c(1,1.4))

#g-index plot... NOT EASY TO REPRESENT!
#ggplot(pubs, aes(x = as.numeric(row.names(pubs)), y = sqrt(sums))) +
#  geom_segment(aes(x = gindex, y = 0, xend = gindex, yend = gindex),
#               size = 0.1, color = "#008080") +
#  geom_line(size = 1, colour = "grey") +
#  geom_abline(intercept = 0, slope = 1, colour = "#008080", linetype = "dashed")
```

Between 2015 and 2017 my contracts were teaching based, with little time for research. Since 2018, however, I have focused increasingly more on research.

I have published (or have in press) `r nrow(pubs)-4` journal articles. In most of these I have done all statistical analyses, and 12 are as first or last author. To date, my articles have been cited `r citSum` times, `r citRecentSum` (`r label_percent()(citRecentProp[1,1])`) since the beginning of `r yearRecent` (see figure below), and `r numbers_to_words(count50cit)` have been cited over 50 times. I have an h-index of `r profile$h_index` and a g-index of `r gindex`[^2].

[^2]: Citation data obtained using the [`scholar`](https://cran.r-project.org/web/packages/scholar/index.html) R package.

```{r echo=FALSE, fig.height=3, fig.width=7.3}
annotate_figure(p.fin, bottom = text_grob(paste0("Source for citation data: Google Scholar. Updated ", 
                                       format(Sys.Date(),'%B %d, %Y')),
                hjust = 1, x = 1, size = 6))
```

## \textbf{Preprints and Articles under Review}

```{=tex}
\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
```
::: {#refs_working_paper}
:::

```{=tex}
\endgroup
```

## \textbf{Published and Accepted Journal Articles}

```{=tex}
\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
```
::: {#refs_journals}
:::

```{=tex}
\endgroup
```

## \textbf{Divulgation articles}

```{=tex}
\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
```
::: {#refs_divulgation}
:::

```{=tex}
\endgroup
```

# Investigación Abierta (YouTube channel)

```{r include=FALSE}
library(tuber)

yt_oauth(scope = "own_account_readonly",
         "D:/GitHub/JDL_CV-master/.httr-oauth")

a <- list_channel_resources(filter = c(channel_id = "UCs-6iLG3cnZwtGFcvyObPpA"), part="contentDetails")

# Uploaded playlists:
playlist_id <- a$items[[1]]$contentDetails$relatedPlaylists$uploads

# Get videos on the playlist
vids <- get_playlist_items(filter= c(playlist_id=playlist_id)) 

# Video ids
vid_ids <- as.vector(vids$contentDetails.videoId)

# Function to scrape stats for all vids
get_all_stats <- function(id) {
  get_stats(id)
} 

# Get stats and convert results to data frame 
res <- lapply(vid_ids, get_all_stats)
res_df <- do.call(rbind, lapply(res, data.frame))

library(dplyr)
res_df <- res_df %>%
  select(-id) %>%
  mutate_if(is.character,as.numeric) %>%
  mutate(proplike = likeCount/(likeCount + dislikeCount))

aveLikeCount <- round(mean(res_df$likeCount), 0)
aveLikePerc <- scales::percent(mean(res_df$proplike),
                               accuracy = 0.1)

stats <- get_channel_stats(channel_id="UCs-6iLG3cnZwtGFcvyObPpA")
subscribers <- stats$statistics$subscriberCount
viewCount <- stats$statistics$viewCount
numVids <- stats$statistics$videoCount
```

[\textcolor{red}{\faYoutubePlay} Investigación Abierta](https://www.youtube.com/c/InvestigaciónAbierta) [\textit{Open Research}] is a YouTube channel (in Spanish) where I post videos and tutorials related to quantitative research methods and open science, as well as useful open source software since 2020. To date (`r format(Sys.Date(),'%B %d, %Y')`), I have posted `r as.numeric(numVids)-1` videos, that have been watched a total of `r prettyNum(as.numeric(viewCount),big.mark=",",scientific=FALSE)` times. The channel has `r prettyNum(as.numeric(subscribers),big.mark=",",scientific=FALSE)` subscribers, and videos have an average of `r prettyNum(as.numeric(aveLikeCount),big.mark=",",scientific=FALSE)` likes, `r prettyNum(mean(res_df$viewCount),big.mark=",",scientific=FALSE, digits=0)` views, and `r aveLikePerc` of ratings are likes[^3].

[^3]: Data obtained using the [`tuber`](https://cran.r-project.org/web/packages/tuber/index.html) R package.

```{=tex}
\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
```
::: {#refs_IA}
:::

```{=tex}
\endgroup
```

# Conference Presentations, Posters and Workshops

```{=tex}
\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
```
`r knitr::knit_child("data/poster.txt")`

```{=tex}
\endgroup
```

# Postgraduate and undergraduate Supervision

The Faculty of Psychology at Universidad El Bosque does not offer research degrees, and all M-level courses are professional masters. Because of this, opportunities to supervise postgraduate students are limited, and most of my postgraduate supervision has been external.

```{r supervision}
ezpickr::pick("data/supervision.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why,
                          .protect = FALSE)
```

# Editorial Appointments

My verified review record is available from my [Publons](https://publons.com/researcher/1333339/juan-david-leongomez/) profile.

```{r service}
ezpickr::pick("data/service.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

# Organisation of International Conferences

```{r event}
ezpickr::pick("data/event.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

# Memberships

## Current

-   [International Society for Human Ethology (ISHE)](https://ishe.org/)

## Past

-   [European Human Behaviour and Evolution Association (EHBEA)](https://www.cambridge.org/core/membership/ehbea)
-   [Association for Psychological Science (APS)](https://www.psychologicalscience.org/)

<!-- *`r Sys.Date()`* -->
